Semantic prediction in {R}ussian

### 2020-04-10 paper.tex
add hlines to headers in tables
Updates from Overleaf

\begin{document}
\hypersetup{allcolors = blue}
\maketitleabstract

% TODO: convert citations and references to bibtex
\nocite{*}

@@

% TODO: clarify introduction: is this article about semantic
% prediction, or about modeling cloze task performance?
Nowadays language models are the most powerful instrument to transfer knowledge. Mostly pre-trained neural network models are more accurate in any type of tasks. This tendency in language processing - usage of language model (LM) weights as a part of base model weights - took place after word2vec announcing. Today there are three main ways to use pre-trained LM in different natural language processing tasks. 
\begin{itemize}
	\item Use pre-trained LM as universal embedder for text/sentence
	\item Fit pre-trained LM on new data (domain adaptation) and also use as an embedder
	\item Fit pre-trained LM as a part of more complex and specific model
\end{itemize}
It is important to note that the resulting model is very dependent on the quality of the based LM. So a possibility to compare models is also demanded and we propose a new comprehensive way to explore properties of different language models.
Comparing LM is not a new topic. There is a lot of different tasks to measure their quality. It starts with the google analogy task for word2vec \cite{mikolov2013efficient} and now GLUE tasks\cite{wang2018glue} are used for these purposes. However, we want to check the generative ability of a different type of LM and compare them to each other.
One of the the key terms in natural language understanding and speech generation is predictability. In cognitive linguistics, it implies a confidence degree of a language unit (word, part of speech, etc.) that can take next place in the sentence (or text). This property of the token in the context is usually measured in terms of the theory of probability, and it also has some well-known probabilistic properties. For example, the sum of the probabilities of all words which can or cannot (in terms of common sense) “continue” the left context is equal to one. A quarter-century ago these assumptions led to the emergence of the first artificial language models (ALM).

@@

\section{Background}

@@

>>>>

\begin{document}
\maketitleabstract
\nocite{*}

@@

% TODO: clarify introduction: is this article about semantic
% prediction, or about modeling cloze task performance?
Nowadays language models are the most powerful instrument to transfer knowledge. Mostly pre-trained neural network models are more accurate in any type of tasks. This tendency in language processing - usage of language model (LM) weights as a part of base model weights - took place after word2vec announcing. Today there are three main ways to use pre-trained LM in different natural language processing tasks. 
\begin{itemize}
	\item Use pre-trained LM as universal embedder for text/sentence
	\item Fit pre-trained LM on new data (domain adaptation) and also use as an embedder
	\item Fit pre-trained LM as a part of more complex and specific model
\end{itemize}
It is important to note that the resulting model is very dependent on the quality of the based LM. So a possibility to compare models is also demanded and we propose a new comprehensive way to explore properties of different language models.
Comparing LM is not a new topic. There is a lot of different tasks to measure their quality. It starts with the google analogy task for word2vec \cite{mikolov2013efficient} and now GLUE tasks\cite{Wang2018GLUEAM} are used for these purposes. However, we want to check the generative ability of a different type of LM and compare them to each other.
One of the the key terms in natural language understanding and speech generation is predictability. In cognitive linguistics, it implies a confidence degree of a language unit (word, part of speech, etc.) that can take next place in the sentence (or text). This property of the token in the context is usually measured in terms of the theory of probability, and it also has some well-known probabilistic properties. For example, the sum of the probabilities of all words which can or cannot (in terms of common sense) “continue” the left context is equal to one. A quarter-century ago these assumptions led to the emergence of the first artificial language models (ALM).

@@

% TODO (@SEMEN SOROKIN) объединить с интродакшн, мб как-то связать или убрать вообще, т.к. абзац незаконченный.
\section{Background}

@@

\section{Related work}
% TODO (@Anastasia Nikiorova) Add article reviews for related works

There are several scientific papers that propose different algorithms for cloze answer generation. In \cite{zhou-cloze} the authors state the importance of next word prediction in language modelling and its potential contribution to OCR and hand writing recognition. The authors enhance existing models with ELMo and BERT language models and train on the CLOTH dataset of cloze tests. Expectedly, BERT models show the highest performance (0.86 and 0.83 accuracy scores on test dataset for BERT Large and BERT Base consecutively), as this model was initially trained to recover masked tokens in text.
